\section{The \emph{Single Parameter} Pareto}\label{sec:theSPP}
Philbrick's Single Parameter Pareto (SPP) is a special case of the Pareto Type~I distribution which has the following cumulative distribution function:
\begin{equation}
F(x) = 1 - \left(\frac{k}{x} \right)^a\label{eqn:Pareto1}
\end{equation}
Many readers are often confused by the reference to the \emph{single parameter}. After all, \philbrick, in Section~III initially presents the Pareto with two parameters (Equation \ref{eqn:Pareto1}), $k$ and $a$, and then later adds that claims should be ``normalized'' by dividing by the ``selected lower bound''

This presentation leaves many readers not understanding how the lower bound,~$k$,  lost its parameter status. Philbrick explains that this is because:
\begin{quote}
	Although there may be situations where this value must be estimated, in virtually all insurance applications this value will be selected in advance. (Section III)
\end{quote}
This explanation often leaves readers less than satisfied.

I offer the alternative that users of the SPP model should consider the process of normalizing the claims to be a transformation of the data rather than the application of a parameter. An analogous transformation occurs when we take $\log$s. When we do that, we do not consider the base of the logarithm to be a parameter. Similarly, we will not consider the lower bound to be a parameter.

To improve clarity of this concept, we present the following:

\begin{table}[h!]
	\centering
	\begin{tabular}[h]{ccc}
		\toprule
		\multirow{3}{*}{Random Variable}& Observed & Normalized\\
		& Claim & Claims\\
		& Amount & Amount \\ \midrule
		Symbol & $\mathbf{Y}$ & $\mathbf{X}$\\ \midrule
		\multirow{2}{*}{Transformation} & & $\mathbf{X}$  =  $g(\mathbf{Y})$\\
		& & $g(\mathbf{Y}) =   \mathbf{Y}/\text{lower bound}$  \\ \midrule
		Domain & [\text{lower bound}, $\infty$] & [1, $\infty$]\\ \midrule
		Density & $a \dfrac{k^a}{y^{a+1}}$ & $qx^{-(q+1)}$\\ \midrule
		Parameters & $k>0$ (scale); $a>0$ (shape)& $q>0$ (shape)\\ 
	\bottomrule
	\end{tabular}
	\caption{The Pareto Type I and the SPP}\label{tbl:PIvSpp}			
\end{table}
We can now work with model forms in the space of $\mathbf{X}$ and then use $g^{-1}$ to transform back into the space of $\mathbf{Y}$. We can also now present the density and distribution functions.

\begin{align}
		f(x) & =  qx^{-(q+1)}\label{SPPf}\\
		F(x) & =  1 - x^{-q}\label{SPPF}
\end{align}

\subsection{Tail weight and the SPP}
The appropriate application of the SPP is in the modeling of claims in the tail of a distribution. The SPP is generally used where the tail is said to be ``thick'' or ``heavy.'' We can measure tail weight based on the change in claim size per unit change in the distribution percentile. Specifically, we calculate the following measure of tail weight:
\begin{equation}\label{tailWt}
\frac{x(p_1) / x(p_0)}{p_1 - p_0}
\end{equation}
In this section, we compare the tail weight of the Pareto to that of the lognormal distribution.

We also note that the mode of the SPP is at its minimum value of $x = 1$. Conversely, for the lognormal, the mode is right of its minimum value of  of $x = 0$.

In  Appendix \ref{ParetoF}, we provide the derivation of the distribution function (Equation (\ref{SPPF})).

\subsection{Other Pareto Forms}
In Appendix \ref{ParetoInventory}, we provide an inventory of Pareto distributions including the SPP presented in Equations (\ref{SPPf}) and (\ref{SPPF}). 

\section{Actuarial Formul\ae}
In general, we leave formula derivation to the Appendices of this paper. In Appendix \ref{derive:ParetoEV}, we present the derivation of the expected value:

\begin{equation}
\mathbb{E}[X]  = 
\begin{cases}
\dfrac{q}{q-1},& \text{if } q > 1\\
\text{undefined},& \text{if } q \leq 1\\         
\end{cases}
\end{equation}
